Structured Versus Decorated Cospans

### 2020-11-23 cospans.tex
unit categor

a\ar[r,"1_a"] & a & a,\ar[l,"1_a"'] & \bot_a:=1\xrightarrow{\phi_0}F(0)\xrightarrow{F(!_a)}F(a)

@@

$$x\odot y:= 1\cong1 \times 1 \xrightarrow{x \times y} F(m) \times F(n) \xrightarrow{\phi_{m,n}} F(m+n) \xrightarrow{F(\psi)} F(m+_{b}n)$$

@@

\node (D) at (3,0) {$1 \cong 1 \times 1$};

@@

The associator $\alpha \colon \odot (\odot \times 1) \Rightarrow \odot (1 \times \odot)$ is formed as follows: for three composable horizontal 1-cells
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$M_1=a$};
\node (B) at (1,0) {$m_1$};
\node (C) at (2,0) {$b$};
\node (D) at (1,-0.5) {$x_1 \in F(m_1)$};
\node (E) at (3,0) {$M_2=b$};
\node (F) at (4,0) {$m_2$};
\node (G) at (5,0) {$c$};
\node (H) at (4,-0.5) {$x_2 \in F(m_2)$};
\node (I) at (6,0) {$M_3=c$};
\node (J) at (7,0) {$m_3$};
\node (K) at (8,0) {$d$};
\node (L) at (7,-0.5) {$x_3 \in F(m_3)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B)
(E) edge node[above]{$i'$} (F)
(G) edge node[above]{$o'$} (F)
(I) edge node[above]{$i''$} (J)
(K) edge node[above]{$o''$} (J);
\end{tikzpicture}
\]
the isomorphism $(M_1\odot M_2)\odot M_3\cong M_1\odot (M_2\odot M_3)$ is the isomorphism of cospans 
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0.5) {$a$};
\node (A') at (0,-0.5) {$a$};
\node (B) at (1.5,0.5) {$(m_1+_{b} m_2)+_{c} m_3$};
\node (C) at (3,0.5) {$d$};
\node (C') at (3,-0.5) {$d$};
\node (D) at (1.5,-0.5) {$m_1+_{b}(m_2 +_{c} m_3)$};
\node (E) at (5.5,0.5) {$(x_1 \odot x_2) \odot x_3 \in F((m_1+_{b} m_2)+_{c} m_3)$};
\node (F) at (5.5,-0.5) {$x_1 \odot (x_2 \odot x_3) \in F(m_1+_{b} (m_2 +_{c} m_3))$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$$} (B)
(C) edge node[above]{$$} (B)
(A) edge node[left]{$\id_a$} (A')
(C) edge node[right]{$\id_d$} (C')
(A') edge node {$$} (D)
(C') edge node {$$} (D)
(B) edge node [left] {$\stackrel{\alpha}{\cong}$} (D);
\end{tikzpicture}
\]
together with an isomorphism $F(\alpha)((x_1 \odot x_2) \odot x_3) \cong (x_1 \odot (x_2 \odot x_3))$ between the decorations 
\begin{gather*}
\scalebox{.8}{$1\xrightarrow{x_1\times x_2}F(m_1)\times F(m_2)\xrightarrow{\phi}F(m_1+m_2)\to F(m_1+_bm_2)\xrightarrow{1\times x_3}F(m_1+_bm_2)\times F(m_3)\xrightarrow{\phi}F((m_1+_bm_2)+m_3)\to F((m_1+_bm_2)+_cm_3)\cong F(m_1+_b(m_2+_cm_3))$} \\
\scalebox{.8}{$1\xrightarrow{x_2\times x_3}F(m_2)\times F(m_3)\xrightarrow{\phi}F(m_2+m_3)\to F(m_2+_cm_3)\xrightarrow{x_1\times1}F(m_1)\times F(m_2+_cm_3)\xrightarrow{\phi}F(m_1\times(m_2+_cm_3))\to F(m_1+_b(m_2+_cm_3))$}
\end{gather*}
which is constructed by pasting structure isomorphisms like above. Similarly the right and left unitors can be constructed, and all data satisfy the axioms of a double category. For full details of these arguments, see \cite[Theorem~4.1.1]{CourserThesis}.
\begin{comment}
 The definition of double category may be found in Definition \ref{defn:double_category}. To show that the pseudofunctor $F$ in the theorem statement induces a double category $F\lCsp$, we must first define the category of objects $F\lCsp_0$, the category of arrows $F\lCsp_1$, as well as the four structure functors which tie them together: the source and target functors $S,T \colon F\lCsp_1 \to F\lCsp_0$, the unit functor $U \colon F\lCsp_0 \to F\lCsp_1$ and the composition functor $\odot$ which says how to compose two composable horizontal 1-cells or two composable 2-morphisms horizontally: $$\odot \colon F\lCsp_1 \times_{F\lCsp_0} F\lCsp_1 \to F\lCsp_1.$$

@@

In more detail, if $(\phi,\phi_0)$ is the lax monoidal structure of the pseudofunctor $F$ as recalled in \cref{subsec:bicats}, the induced monoidal structure on the total Grothendieck category $\X=\inta F$ (\cref{def:GrothCat}) is given by
\begin{equation}\label{eq:explicitstructure2}
\Big(a,x\in F(a)\Big)\ot_{\X}\Big(b,y\in F(b)\Big)=\Big(a+b,\phi_{a,b}(x,y)\in F(a+b)\Big), \qquad I_{\X}=\Big(0_A,\phi_0\Big)
\end{equation}
Moreover, each fibre category $\X_a=F(a)$ obtains a monoidal structure via 
\begin{equation}\label{eq:explicitstructure1}
\otimes_a\maps F(a)\times F(a)\xrightarrow{\phi_{a,a}}F(a+a)\xrightarrow{F(\nabla)}F(a),\quad
I_a\maps\mathbf{1}\xrightarrow{\phi_0}F(0)\xrightarrow{F(!)}F(a)
\end{equation}
where $\nabla$ is the fold map. 
\end{proof}

@@

Building up to an isomorphism of the above described double categories, we now define a double functor
\begin{displaymath}
\lE=(\lE_0,\lE_1)\maps _L\lCsp(\inta F) \longrightarrow F\lCsp
\end{displaymath}
which on vertical categories acts as the identity $\lE_0 = \id_{\A}$. Given a horizontal 1-cell in $_L\lCsp(\inta F)$ as in \cref{eq:scsphor1cell}, $\lE_1$ maps it to the decorated cospan $i\maps a\to m\leftarrow b:o$ with decoration $x\in F(m)$,
whereas a 2-morphism of $L$-structured cospans as above is mapped to the underlying map of cospans in $\A$
%%% We should call these "cospan 2-morphism"s maps of cospans to be consistent with previous work
%%% Alright!
\begin{displaymath}
\begin{tikzcd}
a\ar[r,"i"]\ar[d,"f"'] & m\ar[d,"k"] & b\ar[l,"o"']\ar[d,"g"] \\
a'\ar[r,"i'"']& m' & b'\ar[l,"o'"]
\end{tikzcd}
\end{displaymath}
in $\A$ along with the map $\tau\maps Fk(x)\to x'$ in $F(m')$, namely an $F$-decorated cospan 2-morphism. 
With these definitions, $\lE$ is indeed a (pseudo) double functor as in \cref{def:doublefun}: both $\lE_0$ and $\lE_1$ are functors that appropriately commute with sources and targets, and there exist globular 2-isomorphisms $\lE(M) \odot \lE(N) \simrightarrow\lE(M \odot N)$, $U_{\lE m} \simrightarrow\lE(U_m)$
for any pair of composable horizontal 1-cells $M=\cspn{(a,\bot_a)}{(m,x)}{(b,\bot_b)}{}{}$ and $N=\cspn{(b,\bot_b)}{(n,y)}{(c,\bot_c)}{}{}$ and any object $m$ of $_L\lCsp(\inta F)$. Explicitly, $\mathbb{E}(M)\odot \mathbb{E}(N)$ is given as in \cref{eq:dcospanscomposition} via the pushout cospan and decoration
\begin{equation}\label{eq:1}
 \begin{tikzcd}
  & m+_bn & \\
  a\ar[ur] && b,\ar[ul]
 \end{tikzcd}\qquad
  \mathbf{1}\xrightarrow{x\times y}F(m)\times F(n)\xrightarrow{\phi_{m,n}}F(m+n)\xrightarrow{F(\psi)}F(m+_bn)
\end{equation}
whereas first composing $M$ and $N$ in $_L\lCsp(\inta F)$ using pushouts in $\inta F$ as in \cref{eq:globalpushout} produces 
\begin{displaymath}
 \begin{tikzcd}[column sep={.7in,between origins}]
 && (m+_b n,F(\sigma_m)x+_{(\bot_{m+_bn})}F(\sigma_n)y) && \\
 & (m,x) \ar[ur] && (n,y)\ar[ul] \\
 (a,\bot_a)\ar[ur] && (b,\bot_b)\ar[ur]\ar[ul] && (c,\bot_c)\ar[ul]
 \end{tikzcd}
\end{displaymath}
where $\sigma$ are the canonical maps into the pushout. %overusing notation, streamline with earlier
Under $\lE$ this is mapped to the underlying $\A$-cospan $\cspn{a}{m+_bn}{b}{}{}$ with decoration $F(\sigma_m)x+F(\sigma_n)y$, since a pushout over an initial object is really a coproduct. That decoration is isomorphic to that of \cref{eq:1} due to the following diagram 
\begin{equation}\label{eq:isomorphismdiag}
 \begin{tikzcd}
F(m)\times F(n)\ar[rr,"\phi"]\ar[d,"F(\sigma_m)\times F(\sigma_n)"']\ar[dr,phantom,"\cong"] && F(m+n)\ar[d,"F(\psi)"]\ar[d,bend right=50, phantom,"\cong"']\ar[dl,"F(\sigma_m+\sigma_n)"description] \\
F(m+_bn)\times F(m+_bn)\ar[r,"\phi"'] & F\left((m+_bn)+(m+_bn)\right)\ar[r,"F(\nabla)"'] & F(m+_bn)
 \end{tikzcd}
\end{equation}
where the bottom composite is the fibrewise coproduct in $F(m+_bn)$ as in \cref{eq:explicitstructure1}. The left-hand side isomorphism is due to pseudonaturality of $\phi$ whereas the right-hand side isomorphism follows from universal properties and pseudofunctoriality of $F$.
Regarding identities, the identity horizontal 1-cell $U_m$ in $_L\lCsp(\inta F)$ is $\cspn{(m,\bot_m)}{(m,\bot_m)}{(m,\bot_m)}{}{}$ with $1_m$ as the $A$-component and isomorphisms between initial objects in the fibres. Thus $\lE(U_m)$ is the identity cospan in $A$ together with the `initial decoration' $\bot_m\in F(m)$, and so is $U_{\mathbb{E}(m)}$ as in \cref{eq:UFCsp}. %Do we want to check that E is a double functor one last time?

@@

Since both double categories are symmetric monoidal under the running assumptions (\cref{DC,thm:SC}), we will now show that this double isomorphism is a symmetric monoidal one, namely $\lE=(\lE_0,\lE_1)$ is a symmetric strong monoidal double functor as per \cref{defn:monoidal_double_functor}. Indeed, $\lE_0=\mathrm{id}_\A$ is a braided monoidal functor trivially. For $\lE_1$, given two structured cospans $M=(a,\bot_a)\to(m,x)\leftarrow(b,\bot_b)$ and $M'=(a',\bot_{a'})\to(m',x')\leftarrow(b',\bot_{b'})$ in $_L\lCsp(\inta F)$, we compute the appropriate decorated cospans
\begin{align*}
\lE(M)\ot\lE(M')&\;\stackrel{\cref{eq:tensordecoration}}{=}\;a+a'\xrightarrow{i+i'}m+m'\xleftarrow{o+o'}b+b' \textrm{ with }\mathbf{1}\xrightarrow{x\times x'}F(m)\times F(m')\xrightarrow{\phi_{m,m'}}F(m+m') \\
\lE(M\ot M')&\;\stackrel{\cref{eq:tensorstuctured}}{=}\;\lE\Big((a+a',\bot_{a+a'})\to\underbrace{(m+m',F(\iota_m)x+F(\iota_{m'})x')}_{\cref{eq:fibrewisecoprod}}\leftarrow(b+b',\bot_{b+b'})\Big)%=a+a'\xrightarrow{i+i'}m+m'\xleftarrow{o+o'}b+b' \textrm{ with }\phi_{m,m'}(x,x')
\end{align*}
which are uniquely isomorphic $F(\iota_m)x+F(\iota_{m'})\cong \phi_{m,m'}(x,x')$ in an analogous way to \cref{eq:isomorphismdiag}, as also discussed after \cref{cor:fcocMonGroth}.
Moreover, the monoidal unit for the category of arrows of $F\lCsp$ is $0_\A\xrightarrow{\raisebox{-3pt}[0pt][0pt]{$=$}}0_\A\xleftarrow{\raisebox{-3pt}[0pt][0pt]{$=$}}0_\A$ with the trivial decoration $\phi_0\maps \mathbf{1}\to F(0_A)$,
which is an initial object and as such isomorphic to $0_{F(0)}$
%=\lE((0_A,)\xrightarrow{\raisebox{-3pt}[0pt][0pt]{$=$}}(0_A,\phi_0)\xleftarrow{\raisebox{-3pt}[0pt][0pt]{$=$}}(0_A,\phi_0))$
again by \cref{eq:explicitstructure2} and the discussion after \cref{cor:fcocMonGroth}.
It can be verified that with the above structure, $\lE_1$ is also a braided monoidal functor, and the rest of the axioms of \cref{defn:monoidal_double_functor} hold.
\end{proof}

>>>>

a\ar[r,"1_a"] & a & a,\ar[l,"1_a"'] & \bot_a:=\one\xrightarrow{\phi_0}F(0)\xrightarrow{F(!_a)}F(a)

@@

$$x\odot y:= \one\cong\one \times \one \xrightarrow{x \times y} F(m) \times F(n) \xrightarrow{\phi_{m,n}} F(m+n) \xrightarrow{F(\psi)} F(m+_{b}n)$$

@@

\node (D) at (3,0) {$\one \cong \one \times \one$};

@@

The associator $\alpha \colon \odot (\odot \times 1) \Rightarrow \odot (1 \times \odot)$ is formed as follows: for three composable horizontal 1-cells
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$M_1=a$};
\node (B) at (1,0) {$m_1$};
\node (C) at (2,0) {$b$};
\node (D) at (1,-0.5) {$x_1 \in F(m_1)$};
\node (E) at (3,0) {$M_2=b$};
\node (F) at (4,0) {$m_2$};
\node (G) at (5,0) {$c$};
\node (H) at (4,-0.5) {$x_2 \in F(m_2)$};
\node (I) at (6,0) {$M_3=c$};
\node (J) at (7,0) {$m_3$};
\node (K) at (8,0) {$d$};
\node (L) at (7,-0.5) {$x_3 \in F(m_3)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B)
(E) edge node[above]{$i'$} (F)
(G) edge node[above]{$o'$} (F)
(I) edge node[above]{$i''$} (J)
(K) edge node[above]{$o''$} (J);
\end{tikzpicture}
\]
the isomorphism $(M_1\odot M_2)\odot M_3\cong M_1\odot (M_2\odot M_3)$ is the isomorphism of cospans 
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0.5) {$a$};
\node (A') at (0,-0.5) {$a$};
\node (B) at (1.5,0.5) {$(m_1+_{b} m_2)+_{c} m_3$};
\node (C) at (3,0.5) {$d$};
\node (C') at (3,-0.5) {$d$};
\node (D) at (1.5,-0.5) {$m_1+_{b}(m_2 +_{c} m_3)$};
\node (E) at (5.5,0.5) {$(x_1 \odot x_2) \odot x_3 \in F((m_1+_{b} m_2)+_{c} m_3)$};
\node (F) at (5.5,-0.5) {$x_1 \odot (x_2 \odot x_3) \in F(m_1+_{b} (m_2 +_{c} m_3))$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$$} (B)
(C) edge node[above]{$$} (B)
(A) edge node[left]{$\id_a$} (A')
(C) edge node[right]{$\id_d$} (C')
(A') edge node {$$} (D)
(C') edge node {$$} (D)
(B) edge node [left] {$\stackrel{\alpha}{\cong}$} (D);
\end{tikzpicture}
\]
together with an isomorphism $F(\alpha)((x_1 \odot x_2) \odot x_3) \cong (x_1 \odot (x_2 \odot x_3))$ between the decorations 
\begin{gather*}
\scalebox{.8}{$\one\xrightarrow{x_1\times x_2}F(m_1)\times F(m_2)\xrightarrow{\phi}F(m_1+m_2)\to F(m_1+_bm_2)\xrightarrow{1\times x_3}F(m_1+_bm_2)\times F(m_3)\xrightarrow{\phi}F((m_1+_bm_2)+m_3)\to F((m_1+_bm_2)+_cm_3)\cong F(m_1+_b(m_2+_cm_3))$} \\
\scalebox{.8}{$\one\xrightarrow{x_2\times x_3}F(m_2)\times F(m_3)\xrightarrow{\phi}F(m_2+m_3)\to F(m_2+_cm_3)\xrightarrow{x_1\times1}F(m_1)\times F(m_2+_cm_3)\xrightarrow{\phi}F(m_1\times(m_2+_cm_3))\to F(m_1+_b(m_2+_cm_3))$}
\end{gather*}
which is constructed by pasting structure isomorphisms like above. Similarly the right and left unitors can be constructed, and all data satisfy the axioms of a double category -- essentially breaking down to those of the cospan double category of $\A$ and axioms of the lax monoidal pseudofunctor $F$. For full details of these arguments, see \cite[Theorem~4.1.1]{CourserThesis}.
\begin{comment}
 The definition of double category may be found in Definition \ref{defn:double_category}. To show that the pseudofunctor $F$ in the theorem statement induces a double category $F\lCsp$, we must first define the category of objects $F\lCsp_0$, the category of arrows $F\lCsp_1$, as well as the four structure functors which tie them together: the source and target functors $S,T \colon F\lCsp_1 \to F\lCsp_0$, the unit functor $U \colon F\lCsp_0 \to F\lCsp_1$ and the composition functor $\odot$ which says how to compose two composable horizontal 1-cells or two composable 2-morphisms horizontally: $$\odot \colon F\lCsp_1 \times_{F\lCsp_0} F\lCsp_1 \to F\lCsp_1.$$

@@

In more detail, if $(\phi,\phi_0)$ is the lax monoidal structure of the pseudofunctor $F$ as recalled in \cref{subsec:bicats}, the induced monoidal structure on the total Grothendieck category $\X=\inta F$ (\cref{def:GrothCat}) is given by
\begin{equation}\label{eq:explicitstructure2}
\Big(a,x\in F(a)\Big)\ot_{\X}\Big(b,y\in F(b)\Big)=\Big(a+b,\phi_{a,b}(x,y)\in F(a+b)\Big), \qquad I_{\X}=\Big(0_A,\phi_0\Big)
\end{equation}
Moreover, each fibre category $\X_a=F(a)$ obtains a monoidal structure via 
\begin{equation}\label{eq:explicitstructure1}
\otimes_a\maps F(a)\times F(a)\xrightarrow{\phi_{a,a}}F(a+a)\xrightarrow{F(\nabla)}F(a),\quad
I_a\maps\one\xrightarrow{\phi_0}F(0)\xrightarrow{F(!)}F(a)
\end{equation}
where $\nabla$ is the fold map. 
\end{proof}

@@

Building up to an isomorphism of the above described double categories, we now define a double functor
\begin{displaymath}
\lE=(\lE_0,\lE_1)\maps _L\lCsp(\inta F) \longrightarrow F\lCsp
\end{displaymath}
which on vertical categories acts as the identity $\lE_0 = \id_{\A}$. Given a horizontal 1-cell in $_L\lCsp(\inta F)$ as in \cref{eq:scsphor1cell}, $\lE_1$ maps it to the decorated cospan $i\maps a\to m\leftarrow b:o$ with decoration $x\in F(m)$,
whereas a 2-morphism of $L$-structured cospans as above is mapped to the underlying map of cospans in $\A$
%%% We should call these "cospan 2-morphism"s maps of cospans to be consistent with previous work
%%% Alright!
\begin{displaymath}
\begin{tikzcd}
a\ar[r,"i"]\ar[d,"f"'] & m\ar[d,"k"] & b\ar[l,"o"']\ar[d,"g"] \\
a'\ar[r,"i'"']& m' & b'\ar[l,"o'"]
\end{tikzcd}
\end{displaymath}
in $\A$ along with the map $\tau\maps Fk(x)\to x'$ in $F(m')$, namely an $F$-decorated cospan 2-morphism. 
With these definitions, $\lE$ is indeed a (pseudo) double functor as in \cref{def:doublefun}: both $\lE_0$ and $\lE_1$ are functors that appropriately commute with sources and targets, and there exist globular 2-isomorphisms $\lE(M) \odot \lE(N) \simrightarrow\lE(M \odot N)$, $U_{\lE m} \simrightarrow\lE(U_m)$
for any pair of composable horizontal 1-cells $M=\cspn{(a,\bot_a)}{(m,x)}{(b,\bot_b)}{}{}$ and $N=\cspn{(b,\bot_b)}{(n,y)}{(c,\bot_c)}{}{}$ and any object $m$ of $_L\lCsp(\inta F)$. Explicitly, $\mathbb{E}(M)\odot \mathbb{E}(N)$ is given as in \cref{eq:dcospanscomposition} via the pushout cospan and decoration
\begin{equation}\label{eq:1}
 \begin{tikzcd}
  & m+_bn & \\
  a\ar[ur] && b,\ar[ul]
 \end{tikzcd}\qquad
  \one\xrightarrow{x\times y}F(m)\times F(n)\xrightarrow{\phi_{m,n}}F(m+n)\xrightarrow{F(\psi)}F(m+_bn)
\end{equation}
whereas first composing $M$ and $N$ in $_L\lCsp(\inta F)$ using pushouts in $\inta F$ as in \cref{eq:globalpushout} produces 
\begin{displaymath}
 \begin{tikzcd}[column sep={.7in,between origins}]
 && (m+_b n,F(\sigma_m)x+_{(\bot_{m+_bn})}F(\sigma_n)y) && \\
 & (m,x) \ar[ur] && (n,y)\ar[ul] \\
 (a,\bot_a)\ar[ur] && (b,\bot_b)\ar[ur]\ar[ul] && (c,\bot_c)\ar[ul]
 \end{tikzcd}
\end{displaymath}
where $\sigma$ are the canonical maps into the pushout. %overusing notation, streamline with earlier
Under $\lE$ this is mapped to the underlying $\A$-cospan $\cspn{a}{m+_bn}{b}{}{}$ with decoration $F(\sigma_m)x+F(\sigma_n)y$, since a pushout over an initial object is really a coproduct. That decoration is isomorphic to that of \cref{eq:1} due to the following diagram 
\begin{equation}\label{eq:isomorphismdiag}
 \begin{tikzcd}
F(m)\times F(n)\ar[rr,"\phi"]\ar[d,"F(\sigma_m)\times F(\sigma_n)"']\ar[dr,phantom,"\cong"] && F(m+n)\ar[d,"F(\psi)"]\ar[d,bend right=50, phantom,"\cong"']\ar[dl,"F(\sigma_m+\sigma_n)"description] \\
F(m+_bn)\times F(m+_bn)\ar[r,"\phi"'] & F\left((m+_bn)+(m+_bn)\right)\ar[r,"F(\nabla)"'] & F(m+_bn)
 \end{tikzcd}
\end{equation}
where the bottom composite is the fibrewise coproduct in $F(m+_bn)$ as in \cref{eq:explicitstructure1}. The left-hand side isomorphism is due to pseudonaturality of $\phi$ whereas the right-hand side isomorphism follows from universal properties and pseudofunctoriality of $F$.
Regarding identities, the identity horizontal 1-cell $U_m$ in $_L\lCsp(\inta F)$ is $\cspn{(m,\bot_m)}{(m,\bot_m)}{(m,\bot_m)}{}{}$ with $1_m$ as the $A$-component and isomorphisms between initial objects in the fibres. Thus $\lE(U_m)$ is the identity cospan in $A$ together with the `initial decoration' $\bot_m\in F(m)$, and so is $U_{\mathbb{E}(m)}$ as in \cref{eq:UFCsp}. %Do we want to check that E is a double functor one last time?

@@

Since both double categories are symmetric monoidal under the running assumptions (\cref{DC,thm:SC}), we will now show that this double isomorphism is a symmetric monoidal one, namely $\lE=(\lE_0,\lE_1)$ is a symmetric strong monoidal double functor as per \cref{defn:monoidal_double_functor}. Indeed, $\lE_0=\mathrm{id}_\A$ is a braided monoidal functor trivially. For $\lE_1$, given two structured cospans $M=(a,\bot_a)\to(m,x)\leftarrow(b,\bot_b)$ and $M'=(a',\bot_{a'})\to(m',x')\leftarrow(b',\bot_{b'})$ in $_L\lCsp(\inta F)$, we compute the appropriate decorated cospans
\begin{align*}
\lE(M)\ot\lE(M')&\;\stackrel{\cref{eq:tensordecoration}}{=}\;a+a'\xrightarrow{i+i'}m+m'\xleftarrow{o+o'}b+b' \textrm{ with }\one\xrightarrow{x\times x'}F(m)\times F(m')\xrightarrow{\phi_{m,m'}}F(m+m') \\
\lE(M\ot M')&\;\stackrel{\cref{eq:tensorstuctured}}{=}\;\lE\Big((a+a',\bot_{a+a'})\to\underbrace{(m+m',F(\iota_m)x+F(\iota_{m'})x')}_{\cref{eq:fibrewisecoprod}}\leftarrow(b+b',\bot_{b+b'})\Big)%=a+a'\xrightarrow{i+i'}m+m'\xleftarrow{o+o'}b+b' \textrm{ with }\phi_{m,m'}(x,x')
\end{align*}
which are uniquely isomorphic $F(\iota_m)x+F(\iota_{m'})\cong \phi_{m,m'}(x,x')$ in an analogous way to \cref{eq:isomorphismdiag}, as also discussed after \cref{cor:fcocMonGroth}.
Moreover, the monoidal unit for the category of arrows of $F\lCsp$ is $0_\A\xrightarrow{\raisebox{-3pt}[0pt][0pt]{$=$}}0_\A\xleftarrow{\raisebox{-3pt}[0pt][0pt]{$=$}}0_\A$ with the trivial decoration $\phi_0\maps \one\to F(0_A)$,
which is an initial object and as such isomorphic to $0_{F(0)}$
%=\lE((0_A,)\xrightarrow{\raisebox{-3pt}[0pt][0pt]{$=$}}(0_A,\phi_0)\xleftarrow{\raisebox{-3pt}[0pt][0pt]{$=$}}(0_A,\phi_0))$
again by \cref{eq:explicitstructure2} and the discussion after \cref{cor:fcocMonGroth}.
It can be verified that with the above structure, $\lE_1$ is also a braided monoidal functor, and the rest of the axioms of \cref{defn:monoidal_double_functor} hold.
\end{proof}
